\bf Fast Neural Machine Translation Implementation

### 2018-05-17 wnmt.2018/wnmt.tex
turn on timings

We take an opposing approach eschewing model selection in favour efficient implementation. We use and enhanced a custom inference engine, Amun~\citep{junczys2016neural}, which we developed on the premise that fast deep-learning inference is an issue that deserves dedicated tools that are not compromised by competing objectives such as training or support for multiple models. As well as delivering on the practical goal of fast inference, it can serve as a test-bed for novel ideas on neural network inference, and is useful as a means to explore the upper limit of the possible speed for a particular model and hardware. That is, Amun is an inference-only engine that supports a limited number of NMT models that put fast inference on modern GPU above all other considerations. %The consequence of this focused approach can be seen in the results of the shared task ???.

@@

Our second system uses multiplicative-LSTM~\citep{krause2017} in the encoder and the first layer of a decder, and a GRU in the second layer, using an extension of the Nematus~\citep{sennrich-EtAl:2017:EACLDemo} toolkit which supports such models. We trained 2 systems with differing vocabulary sizes and varied the beam sizes before choosing the the settings that produces good translation quality on the validation set, Table~\ref{tab:mLSTM BLEU - vocab sizes}.

>>>>

We take an opposing approach by eschewing model selection in favour of efficient implementation. We use and enhanced a custom inference engine, Amun~\citep{junczys2016neural}, which we developed on the premise that fast deep-learning inference is an issue that deserves dedicated tools that are not compromised by competing objectives such as training or support for multiple models. As well as delivering on the practical goal of fast inference, it can serve as a test-bed for novel ideas on neural network inference, and is useful as a means to explore the upper limit of the possible speed for a particular model and hardware. That is, Amun is an inference-only engine that supports a limited number of NMT models that put fast inference on modern GPU above all other considerations. %The consequence of this focused approach can be seen in the results of the shared task ???.

@@

Our second system uses multiplicative-LSTM~\citep{krause2017} in the encoder and the first layer of a decder, and a GRU in the second layer, trained with an extension of the Nematus~\citep{sennrich-EtAl:2017:EACLDemo} toolkit which supports such models. We trained 2 systems with differing vocabulary sizes and varied the beam sizes before choosing the the settings that produces good translation quality on the validation set, Table~\ref{tab:mLSTM BLEU - vocab sizes}.
